\Title

### 2021-05-12 latex/paper/main.tex
Wrote the conclusion and abstract

%/========== Abstract ==========/%
\begin{abstract}
TODO: Abstract here.
\end{abstract}

\begin{IEEEkeywords}
TODO: keywords in alphabetical order, separated by commas.
\end{IEEEkeywords}

@@

%/========== Conclusion ==========/%
\section{Conclusion}\label{sec:conclusion}
In this article we summarized the existing theory of virtual nonholonomic
constraints (VNHCs) ........
\textbf{TODO conclude nicely}
In the end, we demonstrated that virtual nonholonomic constraints are capable of
injecting and dissipating energy in a robust manner, all while producing
realistic biological motion.

>>>>

%/========== Abstract ==========/%
\begin{abstract}
    In this article we study virtual nonholonomic constraints, which are
    relations between the generalized coordinates and generalized momenta of a
    mechanical system that can be enforced via feedback control.
    We design a constraint which emulates gymnastics giant motion in an
    acrobot, and prove rigorously that this constraint will inject or dissipate
    energy.
    This constraint is tested on a real-world acrobot, demonstrating highly
    effective energy regulation properties and robustness to a variety of
    disturbances.
\end{abstract}

\begin{IEEEkeywords}
    energy regulation, virtual nonholonomic constraints, acrobot, gymnastics.
\end{IEEEkeywords}

@@

%/========== Conclusion ==========/%
\section{Conclusion}\label{sec:conclusion}

In this article we redeveloped the framework of virtual nonholonomic
constraints for underactuated mechanical systems.
We applied this framework towards the acrobot, and designed a constraint which
emulates giant motion from gymnastics.
We proved this constraint will inject energy into the simplified acrobot whose
limbs are massless rods of equal length, with equal masses at the tips.
Then we performed simulations of this VNHC, as well as physical experiments.
These demonstrated that virtual nonholonomic constraints are capable of
injecting and dissipating energy in a robust manner, all while producing
realistic biological motion.
